Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
updated red Xs

%Our approach operates at a level of abstraction above existing pixel-based methods. 
%This allows us to leverage both local and global information to produce more accurate reconstructions. 
With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:biological_constraints}).
Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved region merging for neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect split errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $19.7\%$ while maintaining scalable runtimes for large volumes.

>>>>

%Our approach operates at a level of abstraction above existing pixel-based methods. 
%This allows us to leverage both local and global information to produce more accurate reconstructions. 
With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:teaser_pipeline}).
Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved region merging for neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect split errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $8.2\%$ while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/paper.tex
updated red Xs

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 19.7\%.
\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
\end{abstract}

>>>>

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
\end{abstract}
